Title

### 2012-07-10 inc/external_forces/external_forces.tex
A little more reoganization related to splitting the AG model chapter in two. Futher I have started an introduction to the extension chapter

\subsection{Formal Extension to Include Generic External Forces} \label{sec:external_forces}

\subsubsection{Mathematical Formulation of External Force Contribution}
\ref{eq:potential_integral} is the entry point for the internal Coulombic repulsion force; since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) \rightarrow & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum V_{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum \int d\vecprime{r} V_{ext}(\vec{r}) n(\vecprime{r}; t) \\
    = & \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t)
  \end{split}
\end{equation}
This form of $\Phi(\vec{r};t)$ can be substituted into the definition of $K^{force}$ (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} \rightarrow & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum K^{ext}_{ij}
  \end{split}
\end{equation}
where $K^{int}$ is simply the old $K^{force}$. Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation} \label{eq:Kint}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}

\subsubsection{Constant External Forces}

@@

\subsubsection{Linear External Forces}

@@

\subsubsection{Validity and Limitations}

@@

\subsection{Practical Extension to Include Magnetic Lenses and RF Cavities}

\subsubsection{Region of Influence}

@@

\subsubsection{Magnetic Lenses}

@@

\subsubsection{RF Cavities}

>>>>

\section{Formal Extension to Include Generic External Forces} \label{sec:external_forces}

\subsection{Mathematical Formulation of External Force Contribution}
\ref{eq:potential_integral} is the entry point for the internal Coulombic repulsion force; since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) \rightarrow & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum V_{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum \int d\vecprime{r} V_{ext}(\vec{r}) n(\vecprime{r}; t) \\
    = & \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t)
  \end{split}
\end{equation}
This form of $\Phi(\vec{r};t)$ can be substituted into the definition of $K^{force}$ (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} \rightarrow & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum K^{ext}_{ij}
  \end{split}
\end{equation}
where $K^{int}$ is simply the old $K^{force}$. Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation} \label{eq:Kint}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}

\subsection{Constant External Forces}

@@

\subsection{Linear External Forces}

@@

\subsection{Validity and Limitations}

@@

\section{Practical Extension to Include Magnetic Lenses and RF Cavities}

\subsection{Region of Influence}

@@

\subsection{Magnetic Lenses}

@@

\subsection{RF Cavities}

### 2012-07-10 inc/initial_conditions/initial_conditions.tex
insert commentary from JAP paper to relevant places
A little more reoganization related to splitting the AG model chapter in two. Futher I have started an introduction to the extension chapter

\subsection{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe \cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this paper, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

>>>>

\section{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe \cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this paper, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

### 2012-07-10 main.tex
minor
Added basic chapter/section structure
Added bibliography from model_lenses paper as a starting point. Added abstraction code for a choice between bibtex and biblatex.
removed fontsym.tex as it really was just part of the manual.
Began some of the mathematical sections.
More on MS model
added gaussian distribution section
Renamed subsection title to "Evolution of a Gaussian Distribution", added abbrev. LHS and RHS
Added text to ms_model
switched to import for directory control
worked out some teething issues for import package
Began porting the OE laser paper into the thesis
Began porting

\documentclass{uicthesi}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
%\usepackage{euler}

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}

\title{Title}
\author{Joel Berger}
\pdegrees{of the\\University of Illinois at Chicago}
\degree{Doctor of Philosophy in Experimental Physics}

@@

\listofabbreviations
%\begin{list}
%{}
%{\setlength
%   {\labelwidth}{1in}
%    \setlength{\leftmargin}{1.5in}
%    \setlength{\labelsep}{.5in}
%    \setlength{\rightmargin}{\leftmargin}}
%\item[AMS\hfill] American Mathematical Society
%\item[CTAN\hfill] Comprehensive \TeX\ Archive Network
%\item[TUG\hfill] \TeX\ Users Group
%\item[UIC\hfill] University of Illinois at Chicago
%\item[UICTHESI\hfill] Thesis formatting system for use at UIC.
%\end{list}

@@

%\appendices
%\appendix
%\newpage
%\input fontsym
%\bibformb
%\bibliography{uictman}
%\vita
%This is where the vita goes.  Its organization is left as an exercise.
%Hint: see the list of abbreviations.
\end{document}

>>>>

%This work is licensed under the Creative Commons Attribution-NonCommercial-NoDerivs 3.0 United States License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-nd/3.0/us/ or send a letter to Creative Commons, 444 Castro Street, Suite 900, Mountain View, California, 94041, USA.

\documentclass{uicthesi}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{url}
\usepackage{ifthen}
\usepackage{pgffor}

%\usepackage{euler}
%\usepackage{breqn}

\usepackage[version=3]{mhchem}

\usepackage{import}
\usepackage{subfig}

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\input{mytikz}

%% My convenience fuctions
\providecommand{\vecprime}[1]{\vec{#1}\,^{\prime}}

\providecommand{\smallT}{\ensuremath{{\scriptscriptstyle T}}}
\providecommand{\smallD}{\ensuremath{{\scriptscriptstyle D}}}
\providecommand{\smallF}[0]{ { \scriptscriptstyle F } }
%\providecommand{\smallZ}{\ensuremath{{\scriptscriptstyle Z}}}

\providecommand{\abbr}[2]{\item[#1\hfill] #2}

%% Special handling for using biblatex vs bibtex ==
\newboolean{usebiblatex}
\setboolean{usebiblatex}{false}

\ifthenelse{\boolean{usebiblatex}}{
  \usepackage{biblatex}
  \addbibresource{bibliography.bib}
}{}
%% ==

\title{Title}
\author{Joel Berger}
\pdegrees{of the\\University of Illinois at Chicago}
\degree{Doctor of Philosophy in Physics}

@@

\listofabbreviations
\begin{list}
  {}
  {\setlength{\labelwidth}{1in}
   \setlength{\leftmargin}{1.5in}
   \setlength{\labelsep}{.5in}
   \setlength{\rightmargin}{\leftmargin}}

  \abbr{AG}{Analytic Gaussian (Model)}
  \abbr{AR}{Anti-Reflection}
  \abbr{DC}{Direct Current (i.e. Static Electric Field)}
  \abbr{DTEM}{Dynamic Transmission Electron Microscopy}
  \abbr{FWHM}{Full-Width Half Maximum}
  \abbr{GRIN}{Gradient Index (of Refraction)}
  \abbr{GVD}{Group Velocity Dispersion}
  \abbr{HW1/eM}{Half-Width 1/e Maximum}
  \abbr{LHS}{Left Hand Side}
  \abbr{ML}{Mode-Locked}
  \abbr{Q}{Quality Factor}
  \abbr{RHS}{Right Hand Side}
  \abbr{RF}{Radio Frequency}
  \abbr{SBR}{Saturable Bragg Reflector}
  \abbr{TLS}{Thermal Lens Shaping}
  \abbr{TEM$_{00}$}{Tranvserse ElectroMagnetic 00 Mode}
  \abbr{TM$_{010}$}{Tranvserse Magnetic 010 Mode}
  \abbr{UED}{Ultrafast Electron Diffraction}
  \abbr{UEM}{Ultrafast Electron Microscope}
  \abbr{UIC}{University of Illinois at Chicago}
\end{list}

@@

\chapter{Review of Foundational Modeling Efforts} \label{chap:previous_models}

  \subimport{inc/ms_model/}{ms_model}

\chapter{Extension of the Analytic Gaussian Model\\for UEM Column Modeling}

Modeling a system as complex as an Ultrafast Electron Microscope is a task too large for one person.
In the previous chapter\ref{chap:previous_models} I have highlighted some previous efforts at modeling electron pulse evolution.
While these are excellent works in their own right, none provide the complete picture of the evolution of an electron pulse through the entire column.
In the following chapter I will present a model which builds on and extends those individual pieces to form a single model; one which is generic enough to model many different columns and which is computationally fast enough to be used to design and optimize a column.

  \subimport{inc/liouvilles_theorem/}{liouvilles_theorem}

  \subimport{inc/initial_conditions/}{initial_conditions}

  \subimport{inc/external_forces/}{external_forces}

\section{Model Results, Predictions and Implications} \label{sec:model_results}

\chapter{Prototype Instrument}

  \subimport{inc/laser/}{laser}

\section{Chamber Design}

\section{Accelerator Design}

\section{Magnetic Lenses}

  \subimport{inc/magnetic_lenses/}{maglens}

\section{Deflection Plates}

\chapter{Photocathode Engineering}

\section{Flat Metal Photocathodes}

\section{Nanopatterned (Plasmonic) Photocathodes}

\section{Semiconductor Photocathodes}

  \subimport{inc/semicond/}{semicond}

\chapter{Experimental Results}

%\appendices
%\appendix
%\newpage

%% Special handling for using biblatex vs bibtex ==
\ifthenelse{\boolean{usebiblatex}}{
  \printbibliography
}{
  \bibformc
  \bibliography{bibliography,biblaser}
}
%% ==

%\vita
%This is where the vita goes.  Its organization is left as an exercise.
%Hint: see the list of abbreviations.
\end{document}
